On The Impact of Atoms of Confusion in JavaScript Code

### 2021-04-29 2_Background.tex
minor fixes

These previous studies~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17,DBLP:conf/msr/GopsteinZFC18}
have a greate influence in our work. Even though JavaScript is a dynamic language that differs from \clang in a variety of aspects, it also has a number of constructs in common. In addition, the imperative aspects of the language are syntactically similar to \clang, e.g., assignments, conditional expressions, \texttt{if}-statements, pre and post increments and decrements, among others. On the one hand, this means that some of the atoms of confusion that exist in \clang programs may also occur in JavaScript code. On the other hand, differences between the languages and the surrounding programming cultures may lead to code patterns that are atoms of confusion in one language not being atoms in the other one.
%Although JavaScript allows us to program in different paradigms from the one C follows, most of the JavaScript code found in popular repositories are written under the imperative paradigm. Also, both languages share many syntactical rules, which allows us to replicate some of the C atoms in JavaScript.

@@

Santos and Gerosa~\cite{Santos:2018:ICP} analyze the impact of eleven coding practices on program readability. Although some of these practices, such as avoiding more than three levels of code block nesting, are atom candidates, most of the practices analyzed in their study are more related to code formatting than language constructs or idioms. We borrow from their research the methodology for collecting the opinion of practitioners regarding code snippets preference.

>>>>

These previous studies~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17,DBLP:conf/msr/GopsteinZFC18}
have a great influence in our work. Even though JavaScript is a dynamic language that differs from \clang in a variety of aspects, it also has a number of constructs in common. In addition, the imperative aspects of the language are syntactically similar to \clang, e.g., assignments, conditional expressions, \texttt{if}-statements, pre and post increments and decrements, among others. On the one hand, this means that some of the atoms of confusion that exist in \clang programs may also occur in JavaScript code. On the other hand, differences between the languages and the surrounding programming cultures may lead to code patterns that are atoms of confusion in one language not being atoms in the other one.
%Although JavaScript allows us to program in different paradigms from the one C follows, most of the JavaScript code found in popular repositories are written under the imperative paradigm. Also, both languages share many syntactical rules, which allows us to replicate some of the C atoms in JavaScript.

@@

Santos and Gerosa~\cite{Santos:2018:ICP} analyze the impact of eleven coding practices on program readability. Although some of these practices, such as avoiding more than three levels of code block nesting, are atom candidates, most of the practices analyzed in their study are more related to code formatting than language constructs or idioms. We borrow from their research the methodology for collecting the practitioners opinion about code snippets preference.
